Cosmic web correlations with the shape, spin and peculiar velocties of dark matter halos

### 2013-09-18 paper/main.tex
main.pdf
important note in a figure's caption
paper updated with new plots on what drives the alignment
text describing the simulation

\usepackage[normalem]{ulem}
\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
\newcommand{\SRK}[1]{\textcolor{darkgreen}{\bf SRK: \textit{#1}}}
\newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}

\newcommand{\LCDM}{$\Lambda$CDM~}
\newcommand{\beq}{\begin{eqnarray}}  
\newcommand{\eeq}{\end{eqnarray}}  
\newcommand{\zz}{$z\sim 3$} 
\newcommand{\apj}{ApJ}  
\newcommand{\apjs}{ApJS}  
\newcommand{\apjl}{ApJL}  
\newcommand{\aj}{AJ}  
\newcommand{\mnras}{MNRAS}  
\newcommand{\mnrassub}{MNRAS accepted}  
\newcommand{\aap}{A\&A}  
\newcommand{\aaps}{A\&AS}  
\newcommand{\araa}{ARA\&A}  
\newcommand{\nat}{Nature}  
\newcommand{\physrep}{PhR}
\newcommand{\pasp}{PASP}    
\newcommand{\pasj}{PASJ}    
\newcommand{\avg}[1]{\langle{#1}\rangle}  
\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha}\else{Ly$\alpha$}\fi}}
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc }\fi}}  
\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc }\fi}}
\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm
        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm
        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\lya}{{Lyman$\alpha$~}}
\newcommand{\clara}{{\texttt{CLARA}}~}
\newcommand{\rand}{{\ifmmode{{\mathcal{R}}}\else{${\mathcal{R}}$ }\fi}}  
\newcommand{\hs}{{\hspace{1mm}}}

@@

\cite{Libeskind2013} & V-Web & $1 \hMpc$ & 
filament &$++$ & $>10^{12}$\hMsun\\

@@

In this paper we use groups found with a FOF halo finder.

@@

In this paper we compute the cosmic web on grids of two different
resolutions $256^3$ and $512^3$...

@@

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T1V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T1V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T1V3.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T2V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T2V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T2V3.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T3V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T3V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/256/256_T3V3.ps}
%\caption{Interweb alignment for $256^3$ grid resolution.}
%\end{figure*}

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T1V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T1V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T1V3.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T2V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T2V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T2V3.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T3V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T3V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/512/512_T3V3.ps}
%\caption{Interweb alignment for $512^3$ grid resolution.}
%\end{figure*}

@@

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_V3.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_V3.ps}
%\caption{Shape alignment for the vweb at $256^3$ resolution.}
%\end{figure*}

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_T1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_T1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_T1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_T2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_T2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_T2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_T3.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_T2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_T3.ps}
%\caption{Shape alignment for the tweb at $256^3$ resolution.}
%\end{figure*}

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_V3.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_V3.ps}
%\caption{Shape alignment for the vweb at $512^3$ resolution.}
%\end{figure*}

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_T1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_T1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_T1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_T2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_T2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_T2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_T3.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_T2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_T3.ps}
%\caption{Shape alignment for the tweb at $512^3$ resolution.}
%\end{figure*}

@@

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_V3.ps}
%\caption{Angular momentum alignment with the Vweb for $256^3$ grid resolution.}
%\end{figure*}

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_V3.ps}
%\caption{Angular momentum alignment with the Vweb for $512^3$ grid resolution.}
%\end{figure*}

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_T1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_T2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_T3.ps}
%\caption{Angular momentum alignment with the Tweb for $256^3$ grid resolution.}
%\end{figure*}

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T3.ps}
%\caption{Angular momentum alignment with the Tweb for $512^3$ grid resolution.}
%\end{figure*}

@@

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_V3.ps}
%\caption{Peculiar velocity alignment with the Vweb for $256^3$ grid resolution.}
%\end{figure*}

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_V3.ps}
%\caption{Peculiar velocity alignment with the Vweb for $512^3$ grid resolution.}
%\end{figure*}

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_T1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_T2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_T3.ps}
%\caption{Peculiar velocity alignment with the Tweb for $256^3$ grid resolution.}
%\end{figure*}

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T3.ps}
%\caption{Peculiar velocity alignment with the Tweb for $512^3$ grid resolution.}
%\end{figure*}

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/Mass/vVWeb.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Mass/vTWeb.ps}
%\caption{Median of the peculiar velocity for the two web  and the two grid resolution.}
%\end{figure*}

%\begin{figure*}
%\includegraphics[width=0.35\textwidth]{../tmp/Type/T_Web_256.ps}
%\includegraphics[width=0.35\textwidth]{../tmp/Type/V_Web_256.ps}
%\includegraphics[width=0.35\textwidth]{../tmp/Type/JT_Web_256.ps}
%\includegraphics[width=0.35\textwidth]{../tmp/Type/JV_Web_256.ps}
%\includegraphics[width=0.35\textwidth]{../tmp/Type/vT_Web_256.ps}
%\includegraphics[width=0.35\textwidth]{../tmp/Type/vV_Web_256.ps}
%\caption{From top to bottom: Shape, J, velocities. 256 resolution. Left Tweb, right Vweb}
%\end{figure*}

%\begin{figure*}
%\includegraphics[width=0.35\textwidth]{../tmp/Type/T_Web_512.ps}
%\includegraphics[width=0.35\textwidth]{../tmp/Type/V_Web_512.ps}
%\includegraphics[width=0.35\textwidth]{../tmp/Type/JT_Web_512.ps}
%\includegraphics[width=0.35\textwidth]{../tmp/Type/JV_Web_512.ps}
%\includegraphics[width=0.35\textwidth]{../tmp/Type/vT_Web_512.ps}
%\includegraphics[width=0.35\textwidth]{../tmp/Type/vV_Web_512.ps}
%\caption{From top to bottom: Shape, J, velocities. 512 resolution. Left Tweb, right Vweb}
%\end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.48\textwidth]{../plot3/Type/256_All.png}
\includegraphics[width=0.48\textwidth]{../plot3/Type/256_Big.png}
\caption{Busy plot. Hard to describe.}
\end{figure*}

>>>>

\usepackage[normalem]{ulem}
\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}

\newcommand{\documentname}{paper~}
\newcommand{\LCDM}{$\Lambda$CDM~}
\newcommand{\beq}{\begin{eqnarray}}  
\newcommand{\eeq}{\end{eqnarray}}  
\newcommand{\zz}{$z\sim 3$} 
\newcommand{\apj}{ApJ}  
\newcommand{\apjs}{ApJS}  
\newcommand{\apjl}{ApJL}  
\newcommand{\aj}{AJ}  
\newcommand{\mnras}{MNRAS}  
\newcommand{\mnrassub}{MNRAS accepted}  
\newcommand{\aap}{A\&A}  
\newcommand{\aaps}{A\&AS}  
\newcommand{\araa}{ARA\&A}  
\newcommand{\nat}{Nature}  
\newcommand{\physrep}{PhR}
\newcommand{\pasp}{PASP}    
\newcommand{\pasj}{PASJ}    
\newcommand{\avg}[1]{\langle{#1}\rangle}  
\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha}\else{Ly$\alpha$}\fi}}
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc }\fi}}  
\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc }\fi}}
\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm
        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm
        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\lya}{{Lyman$\alpha$~}}
\newcommand{\clara}{{\texttt{CLARA}}~}
\newcommand{\rand}{{\ifmmode{{\mathcal{R}}}\else{${\mathcal{R}}$ }\fi}}  
\newcommand{\hs}{{\hspace{1mm}}}

@@

\cite{Libeskind2013} & V-Web & $1 \hMpc$ & 
filament &$++$ & $>10^{12}$\hMsun\\
&   & & 
filament &$+$ & $<10^{12}$\hMsun\\
&   & & 
wall & $++$ & all masses\\

@@

In this \documentname we use the Bolshoi volume. This is a simulation
that follows the non-linear evolution of a dark matter density field
on cosmological scales. The volume is a cubic box with 250\hMpc on a
side, the matter density field is sampled with $2048^3$ particles. The
cosmological parameters in the simulation correspond to the results
inferred from WMAP5 data, which are also consistent with the more
recent results of WMAP9. These parameters are $\Omega_m=0.27$,
$\Omega_{\Lambda} =0.73$, $\sigma_8=0.82$, $n_s=0.95$ and $h=0.70$ for the
matter density, cosmological constant, normalization of the power
spectrum, the slope in the spectrum of the primordial matter
fluctuation and the dimensionless Hubble constant. With this
conditions the mass of each dark matter particle in the simulation
corresponds to $m_p=1.4\times 10^{8}$\hMsun.

In this paper we use groups found with a Friends-Of-Friends (FOF) halo
finder using a linking length of $b=0.17$ times the mean interparticle
separation. This choice translates into halos with a density of $570$
times the mean density at $z=0$. The measurements for the shape,
angular momentum and peculiar velocity are done using the set of
particles in each dark matter halo. The definition we use in this
\documentname for the shape comes from the diagonalization of the
reduced inertia tensor.

\begin{equation}
{\mathcal T}_{lm} = \sum_{i}\frac{x_{i,l}x_{i,m}}{R_i^2}, 
\end{equation}
where $i$ is the particle index in the halo and $l,m$ run over the
three spatial indexes  and $R_i^2 = x_{i,1}^2 + x_{i,2}^2 +
x_{i,3}^2$, where the positions are measured with respect to the
center of mass.

The spin is calculated as
\begin{equation}
\vec{J} = \sum_{i}m_p{R_i}\vec{v}_i, 
\end{equation}
where the velocities are also measured with respect to the center of
mass velocity. Finally the peculiar velocity of a halo is computed as the center of
mass velocity.

@@

In this paper we compute the cosmic web on grids of two different
resolutions $256^3$ and $512^3$. In the case for the Tweb we interpolate

@@

@@

@@

@@

@@

\begin{figure*}
\includegraphics[width=0.48\textwidth]{ax_T_cut.pdf}
\includegraphics[width=0.48\textwidth]{ax_V_cut.pdf}
\includegraphics[width=0.48\textwidth]{J_T_cut.pdf}
\includegraphics[width=0.48\textwidth]{J_V_cut.pdf}
\includegraphics[width=0.48\textwidth]{v_T_cut.pdf}
\includegraphics[width=0.48\textwidth]{v_V_cut.pdf}
\caption{The alignment is always taken with respect to the first eigenvector.}
\end{figure*}
